### 2020-06-02 writeup/experiments.tex
sec 4

\begin{table}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf IncTrain} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{39\%} \\
		{\bf LSTM} & \textbf{36\%} & 36\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
	\vspace{-0.2in}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
	\vspace{-0.2in}
\end{minipage}
\end{table}

@@

\textbf{Data efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that adding the alignment module helps reduce the data efficiency ratio to $36\%$.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

@@

>>>>

\begin{table}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf MTL} & {\bf IncTrain} \\
		\midrule
		{\bf MLP}  & 100\% & \textbf{xx\%} \\
		{\bf LSTM} & \textbf{36\%} & xx\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Measuring the data efficiency ratio of muli-task learning.}
	\label{tab:taskonomy}
	\vspace{-0.2in}
\end{minipage}%
\quad
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Sentiment
		analysis}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & \textbf{0.756} & \textbf{0.388} & \textbf{0.738} & \textbf{0.462} \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Single-task learning results can help predict postive or negative transfer in multi-task learning.}
	\label{tab:mtl_better_than_stl}
	\vspace{-0.2in}
\end{minipage}
\end{table}

@@

\textbf{MTL improves data efficiency ratio.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

@@

\textbf{Validation our theory.} In Figure \ref{fig_ablation}, we validate the three components of our theory on the sentiment analysis dataset.
The experimental procedure is left to Appendix \ref{app_it}.

### 2020-06-02 writeup/intro.tex
sec 4

Understanding negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
For instance, the data sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
On the other hand, uneven data sizes or dominating tasks have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
When all tasks are sufficiently similar, it is known that adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
To motivate our study, we describe simulation results for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
In Figure \ref{fig_model_shift_phasetrans}, we observe that negative transfer occurs as (a) tasks become more different; (b) source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
Furthermore, MTL performance is negatively affected when (c) the covariance matrices of the two tasks become more different.
The observations highlight that we need to develop generalization bounds that scale tightly with properties of the data in order to study MTL performance.

>>>>

Understanding negative transfer requires developing tight generalization bounds for both multi-task learning and single-task learning.
In classical Rademacher or VC based theory of multi-task learning \cite{B00,AZ05,M06}, the generalization bounds are usually presented so that the error reduces as the data sizes of all tasks increase.
For instance, the data sizes of all tasks are often assumed to be equal \cite{B00,LPTV09,LPVT11,MPR16}.
On the other hand, uneven data sizes or dominating tasks have been empirically observed as a cause of negative transfer \cite{YKGLHF20}.
%The benefit of learning multi-task representations has also been studied for certain half-spaces \cite{} and sparse regression \cite{}.
When all tasks are sufficiently similar, it is known that adding more labeled data improves the generalization performance for predicting a particular task \cite{WZR20}.
To motivate our study, we describe simulation results for two linear regression tasks solved using a shared linear layer for both tasks and an output layer for each task.
In Figure \ref{fig_model_shift_phasetrans}, we observe that negative transfer occurs as (a) \textit{task similarity}: tasks become more different; (b) \textit{data size}: source/target data size increases.
%\textbf{Task similarity:}
%\textbf{Data sizes:}
%\textbf{Covariate shift:}
Furthermore, MTL performance is negatively affected when (c) \textit{covariate shift}: the covariance matrices of the two tasks become more different.
The observations highlight the need to develop generalization bounds that scale tightly with properties of the data in order to study MTL performance.
